Thread Pool in GeckoDB/BOLSTER

### 2018-07-12 Presentations/Milestone4/presentation.tex
added description to pool_avg plot
Add Summary to presentation 4

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_structure.png}
		Thread Pool System
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{img/pool_queue.png}
		Enqueuing and Waiting for Tasks
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/thread_pool_use.png}
		Thread Pool Usage
	\end{center}
\end{frame}

@@

>>>>

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_structure.png}
	\end{center}
	\begin{center}
		Thread Pool System
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{img/pool_queue.png}
	\end{center}
	\begin{center}
		Enqueuing and Waiting for Tasks
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously on Thread Pool in GeckoDB/BOLSTER}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/thread_pool_use.png}

	\end{center}
	\begin{center}
		Thread Pool Usage
	\end{center}
\end{frame}

@@

\section{Summary}
\begin{frame}
	\begin{center}
		\huge Summary
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Summary}
	\begin{itemize}
		\item Better execution performance as baseline implementation
		\item Constant average waiting time over different pool sizes
		\item Small performance costs for enqueueing and waiting
	\end{itemize}
\end{frame}

\section{Conclusion}
	\begin{frame}
	\begin{center}
		\huge Conclusion
	\end{center}
\end{frame}
